Evaluation of classical correlation functions from 2/3D images on CPU and GPU architectures: introducing CorrelationFunctions.jl

### 2023-08-31 paper-correlations.tex
Fix images

\begin{figure*}[pt]
  \centering
  \subfigure[Ceramic 1]{
    \includegraphics[width=0.3\linewidth]{samples/Ceramic1.png}}
  \hfill
  \subfigure[Ceramic 2]{
    \includegraphics[width=0.3\linewidth]{samples/Ceramic2.png}}
  \hfill
  \subfigure[Ceramic 3]{
    \includegraphics[width=0.3\linewidth]{samples/Ceramic3.png}}
  \vskip\baselineskip
  \includegraphics[width=0.3\linewidth]{samples/s2-xct.png}
  \includegraphics[width=0.3\linewidth]{samples/c2-xct.png}
  \includegraphics[width=0.3\linewidth]{samples/l2-xct.png}
  \vskip\baselineskip
  \includegraphics[width=0.3\linewidth]{samples/surf2-xct.png}
  \includegraphics[width=0.3\linewidth]{samples/surfvoid-xct.png}
  \vskip\baselineskip
  \includegraphics[width=0.3\linewidth]{samples/pore-size-xct.png}
  \includegraphics[width=0.3\linewidth]{samples/chord-length-xct.png}
  \caption[]{Visualization of XCT images and plots of correlation functions for
    these images.}
  \label{fig:real-xct}
\end{figure*}

\begin{figure*}[pt]
  \centering
  \subfigure[Sandstone 1]{
    \includegraphics[width=0.3\linewidth, frame]{samples/sandstone1.png}}
  \hfill
  \subfigure[Sandstone 2]{
    \includegraphics[width=0.3\linewidth, frame]{samples/sandstone2.png}}
  \hfill
  \subfigure[Carbonate 1]{
    \includegraphics[width=0.3\linewidth, frame]{samples/carbonate1.png}}
  \vskip\baselineskip
  \includegraphics[width=0.3\linewidth]{samples/s2-sem.png}
  \includegraphics[width=0.3\linewidth]{samples/c2-sem.png}
  \includegraphics[width=0.3\linewidth]{samples/l2-sem.png}
  \vskip\baselineskip
  \includegraphics[width=0.3\linewidth]{samples/surf2-sem.png}
  \includegraphics[width=0.3\linewidth]{samples/surfvoid-sem.png}
  \vskip\baselineskip
  \includegraphics[width=0.3\linewidth]{samples/pore-size-sem.png}
  \includegraphics[width=0.3\linewidth]{samples/pore-size-sem.png}
  \caption[]{SEM images and plots of correlation functions for these images.}
  \label{fig:real-sem}
\end{figure*}

>>>>

\begin{figure*}[pt]
  \centering
  \subfigure[Ceramic 1]{
    \includegraphics[width=0.3\linewidth]{samples/Ceramic1.png}}
  \hfill
  \subfigure[Ceramic 2]{
    \includegraphics[width=0.3\linewidth]{samples/Ceramic2.png}}
  \hfill
  \subfigure[Ceramic 3]{
    \includegraphics[width=0.3\linewidth]{samples/Ceramic3.png}}
  \vskip\baselineskip
  \includegraphics[width=0.32\linewidth]{samples/s2-xct.png}
  \includegraphics[width=0.32\linewidth]{samples/c2-xct.png}
  \includegraphics[width=0.32\linewidth]{samples/l2-xct.png}
  \vskip\baselineskip
  \includegraphics[width=0.32\linewidth]{samples/surf2-xct.png}
  \includegraphics[width=0.32\linewidth]{samples/surfvoid-xct.png}
  \vskip\baselineskip
  \includegraphics[width=0.32\linewidth]{samples/pore-size-xct.png}
  \includegraphics[width=0.32\linewidth]{samples/chord-length-xct.png}
  \caption[]{Visualization of XCT images and plots of correlation functions for
    these images.}
  \label{fig:real-xct}
\end{figure*}

\begin{figure*}[pt]
  \centering
  \subfigure[Sandstone 1]{
    \includegraphics[width=0.3\linewidth, frame]{samples/sandstone1.png}}
  \hfill
  \subfigure[Sandstone 2]{
    \includegraphics[width=0.3\linewidth, frame]{samples/sandstone2.png}}
  \hfill
  \subfigure[Carbonate 1]{
    \includegraphics[width=0.3\linewidth, frame]{samples/carbonate1.png}}
  \vskip\baselineskip
  \includegraphics[width=0.32\linewidth]{samples/s2-sem.png}
  \includegraphics[width=0.32\linewidth]{samples/c2-sem.png}
  \includegraphics[width=0.32\linewidth]{samples/l2-sem.png}
  \vskip\baselineskip
  \includegraphics[width=0.32\linewidth]{samples/surf2-sem.png}
  \includegraphics[width=0.32\linewidth]{samples/surfvoid-sem.png}
  \vskip\baselineskip
  \includegraphics[width=0.32\linewidth]{samples/pore-size-sem.png}
  \includegraphics[width=0.32\linewidth]{samples/chord-length-sem.png}
  \caption[]{SEM images and plots of correlation functions for these images.}
  \label{fig:real-sem}
\end{figure*}
